---
title: "R Individual Assignment"
author: "Paine (HE Peiwei, 54471952)"
output: 
  pdf_document: 
    latex_engine: xelatex
---
# 1 Introduction and research question
## 1.1 Introduction
This project is intended to conduct social media data analysis of AC Milan Official Twitter, consisting with data collecting, descriptive analysis, dictionary analysis, sentiment analysis and topic model building.

## 1.2 Research Question
How does the Twitter coverage of AC Milan mainly about?


# 2 Data Collecting
Load required packages.
```{r, message=FALSE, warning=FALSE}
library(twitteR)
library(quanteda)
library(RColorBrewer)
library(ggplot2)
library(igraph)
library(slam)
library(reshape2)
library(RTextTools)
library(corpustools)
```
Set up Twitter API, using direct authentication.
```{r echo = F, message=FALSE}
token = '1178611110-Dvkv3jshF3GVEF1hAnOrWavvLPiGhG3gNMHLRQr'
token_secret = 'm7cWEPVKvOIkb2DRIq7CRU1szsmx2nUF3pTTKcjU4lpHX'
consumer_key = "zI5qgBVNoUXJdaF9sT30B4RM1"
consumer_secret = "57C13ROYQnC0OgaWs3i0DUj1CaHUkUosVRQO2zDT8focVq7xVL"
library(twitteR)
options(httr_oauth_cache=T)
setup_twitter_oauth(consumer_key, consumer_secret, token, token_secret)
```
## 2.1 Gather Tweets by harshtags
Catch English tweets about AC Milan, n=5000, and catch Juventus tweets for further comparision.
```{r, warning = F, message = F,eval=FALSE}
acm_tweets <- plyr::ldply(searchTwitter("#acmilan", n=5000, lang="en"), as.data.frame)
acm_tweets=subset(acm_tweets,language=="en")

juv_tweets <- plyr::ldply(searchTwitter("#juventus", n=5000, lang="en"), as.data.frame)
juv_tweets=subset(juv_tweets,language=="en")
```
Use the ACM and JUV tweets, corpus the tweets text and convert into dfm. Remove stopwords to clean the dfm.
```{r, warning = F, message = F}
load("acmtweets.rda")
load("juvtweets.rda")
stopwords = c(stopwords("english"), 'a','"', ',','&','the',"?","-","[","]","(",")","coa","apps","https", "rt", "t.co","who","you","this","too","for","in","by","via","will","and","has","to","don't","/",":",".","#acmilan","0","!","-",",",'"','one','t')
acm_corpus = corpus(acm_tweets$text)
acm_dfm = dfm(acm_corpus,removePunct=T,removeNumbers=T, removeTwitter=T)
acm_dfm = dfm_select(acm_dfm, stopwords,selection=c("remove"),valuetype=c("fixed"))
acm_dfm = dfm_select(acm_dfm,stopwords("english"),"remove")
juv_corpus = corpus(juv_tweets$text)
juv_dfm = dfm(juv_corpus,removePunct=T,removeNumbers=T, removeTwitter=T)
juv_dfm = dfm_select(juv_dfm, stopwords,selection=c("remove"),valuetype=c("fixed"))
juv_dfm = dfm_select(juv_dfm,stopwords("english"),"remove")
```

## 2.2 Get the friends' connections
Get the basic information and friends connection of AC Milan official Twitter. Convert the data into dataframe.
```{r}
u = twitteR::getUser("acmilan")
followings = u$getFriends()
followings.df = plyr::ldply(u$getFriends(), as.data.frame)
```
Convert the followings list into dataframe.
```{r}
friends = u$getFriendIDs()
followings.df = subset(followings.df, id %in% friends)
followings.df = plyr::arrange(followings.df, -followersCount)
ids = head(followings.df$id, 10)
```
Create a function to get a user's friends.
```{r}
followingslist = function(u) {
  message(u$screenName)
  f = u$getFriends()
  f = plyr::ldply(f, as.data.frame)[c("screenName")]
  data.frame(leader=u$screenName, following=f)
}
```
And apply the userlist to the function, and get 2 layers of connections based on AC Milan Twitter. There are totally over 5000 connections.
```{r, eval=FALSE, warning=FALSE, message=FALSE}
userlist = c(u, followings[ids])
userlist
connections = plyr::ldply(userlist, followingslist, .id=NULL)
```
```{r,echo=FALSE, eval=FALSE}
save(connections,file="connections.rda")
saveRDS(connections, file="acmilanconnections.rds")
write.csv(connections, file="acm.csv")
```
```{r}
connections=readRDS("acmilanconnections.rds")
head(connections)
```


# 3 Data analysis
## 3.1 Descriptive Analysis
### 3.1.1 Social Friends Network
To draw a graph of the connections, keep only the people with in-degree over 5, and adjust the label size based on betweenness centrality, color the labels based on clustering, create a circular layout with the Reingold Tilford layout.
```{r}
g = igraph::graph_from_data_frame(connections, directed=F)
g2 = igraph::decompose(g, min.vertices = 50)[[1]]
g2 =induced_subgraph(g2, degree(g2, V(g2), "in")>5)
centrality = betweenness(g2)
V(g2)$label.cex = 0.7 + 0.5 * centrality / max(centrality)
clusters = edge.betweenness.community(g2)$membership
pal = substr(rainbow(length(unique(clusters)), start=0.33, end=1, v=0.5), 1, 7)
layout <- layout.reingold.tilford(g2, circular=F)
plot(g2, vertex.shape="none", 
     vertex.label.font=2, vertex.label.color = pal[match(clusters, unique(clusters))],
     vertex.label.cex=.7, edge.curved=.1,edge.color="gray85")
```
### 3.1.2 Wordcloud Plots
Compare the top 10 features of AC Milan and Juventus. As the results shown, ACM tweets are more related to italian football, while JUV tweets are more related to other european football clubs, especially those with transfer news.
```{r}
topfeatures(acm_dfm, 10)
```
```{r}
topfeatures(juv_dfm, 10)
```
Plot a naive wordcloud of AC Milan to have a brief view.
```{r warning = F, message = F}
textplot_wordcloud(acm_dfm, max.words = 50, random.color = TRUE, rot.per = .25, colors =sample(colors()[2:128], 5), scale = c(5, .4))
```
Comparing word use in different texts. Specifically look at words are
overrepresented in ACM tweets compared to JUV tweets.
```{r}
cmp = corpustools::corpora.compare(acm_dfm, juv_dfm)
cmp = cmp[order(cmp$over, decreasing = F), ]
h = rescale(log(cmp$over), c(1, .6666))
s = rescale(sqrt(cmp$chi), c(.25,1))
cmp$col = hsv(h, s, .33 + .67*s)
head(cmp,1)
```
Then, plot the contrast wordcloud of ACM and JUV in one plot.
```{r}
cmp = arrange(cmp, -termfreq)
with(head(cmp, 60), plotWords(x=log(over), words=term, wordfreq=termfreq, random.y = T, col=col, scale=3))
title(xlab="Contrast of ACM and JUV tweets")
```

## 3.2 Dictionary Analysis
Create a dictionary of 4 concepts, including "FC.Inter", "Napoli", "AS Roma" and "European". Set some keywords for these 4 concepts.
```{r, message=FALSE}
d = dictionary(list(Inter=c("internazionale", "inter*","icardi","pioli","FCIM"),Napoli=c("napoli", "napo*","sarri","mertens"),Roma=c("asroma","*roma","roma","rom*","totti","dzeko","spalletti"),European=c("premie*","engl*", "*liga","champions","madrid","barc*","arsenal","chelsea","mufc","ronaldo","messi")))
acmd = as.data.frame(dfm_lookup(acm_dfm, d))
juvd = as.data.frame(dfm_lookup(juv_dfm, d))
```
Apply the dictionary to the ACM and JUV dataframe, and calculate the frequency.
```{r}
x1=data.frame(lapply(data.frame(acmd), sum))
y1=data.frame(lapply(data.frame(juvd), sum))
all= rbind(x1, y1)
rownames(all) <- c("via ACM","via JUV")
all
```
```{r, echo=FALSE}
Via=c(rep("ACM" , 4) , rep("JUV" , 4))
Content=c("Inter" ,"Napoli","Roma","European")
Percent=c(210,42,114,215,291,197,146,577)
counts=data.frame(Via,Content,Percent)
```
Plot the bar chart with ggplot, to compare the tweets contents of ACM and JUV.
As the plot shown, ACM is mostly interested in FC Inter, which has been its greatest competitor in Serie A from past till nowadays. However, JUV is more related to other european football issues than ACM.
```{r}
ggplot(counts, aes(fill=Content, y=Percent, x=Via)) + geom_bar(stat="identity",position="fill")+scale_fill_manual(values=c("#FFCC33","#000099", "#0099FF", "#990000"))
```

## 3.3 Topic Model
### 3.3.1 Bulid Topic Model
Build a topic model of ACM tweets by using LDA, automatically assigns topics to text documents.
```{r}
d = convert(acm_dfm, to="topicmodels")
m = LDA(d, k = 5, method = "Gibbs", control=list(alpha=.1, iter=100))
ignore = c(stopwords('english'),'acmilan','milan','footballitalia', 'forzamilan','peopl*','americ*')
d = dfm(acm_dfm, remove=ignore, stem=T)
d = convert(d, to="topicmodels")
set.seed(123)
m = LDA(d, k = 5, method = "Gibbs", control=list(alpha=.1, iter=100))

topic=data.frame(terms(m, 10))
colnames(topic) = c("Berlusconi", "Rui Costa", "Rising Star","News","Transfer")
topic
```
```{r, echo=FALSE}
tpd = posterior(m)$topics
tpd=  as.data.frame(tpd)
tpd$id = 1:3313
colnames(tpd) = c("Berlusconi", "Rui Costa", "Rising Star","News","Transfer")
```
Compare with JUV topic model:
```{r,echo=FALSE, message=TRUE}
jd = convert(juv_dfm, to="topicmodels")
jm = LDA(jd, k = 5, method = "Gibbs", control=list(alpha=.1, iter=100))
ignore = c(stopwords('english'),'juventus','footballitalia','team','per','peopl*','americ*')
jd = dfm(juv_dfm, remove=ignore, stem=T)
jd = convert(jd, to="topicmodels")
set.seed(123)
jm = LDA(jd, k = 5, method = "Gibbs", control=list(alpha=.1, iter=100))
jtopic=data.frame(terms(jm, 10))
colnames(jtopic) = c("Bayern", "Serie A", "Transfer","Contract","Compete")
jtopic
```
### 3.3.2 Computing Perplexity
Evaluate the topic model by computing perplexity.
```{r, message=FALSE}
train = d[sample(1:nrow(d), 2400), ]
eval = d[setdiff(1:nrow(d), train), ]

d = list()
for (k in c(10, 25, 50, 100)) {
  message(k)
  for (i in 1:5) {
  m = LDA(train, k = k, method = "Gibbs", control=list(alpha=5/k, iter=100))
  p = perplexity(m, eval)
  d = c(d, list(data.frame(k=k, i=i, p=p)))
  }
}
```
Test the perplexity of train and eval dataset seperately. Perplexity was 58.9 on the training data, and a little higher 60.6 on the evaluation set.
```{r}
perplexity(m, newdata = train)
perplexity(m, newdata = eval)
```
```{r}
d = rbind.fill(d)
d2 = tapply(d$p, d$k, mean)
plot(d$k, d$p, type="l")
```

## 3.4 Sentiment Analysis
### 3.4.1 Applying Sentiment Dictionary to DTM
Read lexicon as dictionary to define positive and negative words.
```{r}
lexicon = readRDS("lexicon.rds")
pos_words = lexicon$word1[lexicon$priorpolarity == "positive"]
neg_words = lexicon$word1[lexicon$priorpolarity == "negative"]
```
Read ACM tweets texts, and apply the sentiment dictionary to create matrix of positive and negative words.
```{r}
textacm=acm_tweets[c("text")]
acmdtm = create_matrix(textacm, language="english",removePunctuation=T, stemWords=F)
acm_tweets$npos = row_sums(acmdtm[, colnames(acmdtm) %in% pos_words])
acm_tweets$nneg = row_sums(acmdtm[, colnames(acmdtm) %in% neg_words])
```
Calculate the sentiment scores.
```{r}
acm_tweets$sent = (acm_tweets$npos - acm_tweets$nneg) / (acm_tweets$npos + acm_tweets$nneg)
acm_tweets$sent[is.na(acm_tweets$sent)] = 0
```
Use quanteda to apply the sentiment dictionary to ACM tweets.
```{r}
dict = dictionary(list(pos=pos_words, neg=neg_words))
dfm2 = dfm(paste(acm_tweets$text), dictionary=dict)
head(dfm2)
```
Convert it to a data.frame and combine it with the tweets, according to the sentiment classification and retweetcount. 
```{r}
d2 = as.data.frame(dfm2)
acm_tweets = cbind(acm_tweets, d2)
acmt=subset(acm_tweets,select=c("id","screenName","text","retweetCount","pos","neg","sent"))
acmt$gold = as.factor(ifelse(acmt$retweetCount > 100, "pos", "neg"))
acmt$pred = ifelse(acmt$sent > 0, "pos", "neg")
m = table(acmt$gold, acmt$pred)
m
```
As the result shown, when the retweetCount is more than 100, there seems to be more negative words in the text. So I guess more negative contents about AC Milan are more easily to spread on Twitter.

### 3.4.2 Validating sentiment

Compute accuracy, precision, and recall on a dichotomized version of the predictions and manual sentiment.
Firstly calculate overall prediction accuracy:
```{r}
sum(diag(m)) / sum(m)
```
Then compute precision, recall and FScore per class. As the FScore is not very high, the coorelation between retweetCount and words sentiment is not very significant.
```{r}
pr = m["pos", "pos"] / sum(m[, "pos"])
re = m["pos", "pos"] / sum(m["pos", ])
f1 = 2*pr*re/(pr+re)
print("FScore:")
c(Precision=pr, Recall=re, FScore=f1)
```


# 4 Conclusion
## 4.1 Social Network Analysis
As the friends connections shown, AC Milan has a close connection with other football clubs and some famous footballers, even sports celebrity in other area like Kobe Bryant, and interestingly, the FIFA is in the center place of this network, and this graph reveals the social network of football world to a certain extent.

## 4.2 Textual Analysis
To conduct the textual analysis, firstly I use JUV tweets to do the comparision. From the wordcloud plots, we could see "footballitalia" is the most frequent neutral word between 2 data sets, and ACM focus on its own team news, while JUV relates to other external news.

Secondly, the dictionary analysis also proved my guess from the simple wordclouds. As the bar graph shown, JUV has more texts related to European football issues, while ACM focus on FC Inter besides its own team news.

Thirdly, from the topic model of ACM tweets, I conclude 5 topics, which are "Berlusconi", "Rui Costa", "Rising Star","News" and "Transfer". Except "Transfer", all the other 4 topics are closely related to the discussion of AC Milan internal news. Comparing with JUV top model, which is hard to classify each topic, ACM model could more qualitative illustrate different topics. And by computing perplexity, the score is around 60, just as the graph shown, 25 is the turning point, which means ACM topic model makes sense.

## 4.3 Sentiment Analysis
By using the lexicon dictionary, I conduct a sentiment analysis of ACM tweets, by testing the correlation between retweetCount and word sentiment. As the result shown, when the retweetCount is more than 100, there seems to be more negative words in the text, which means more negative contents about AC Milan are more easily to spread on Twitter. To validate sentiment analysis result, as the FScore 0.688 is not very high, the coorelation between retweetCount and words sentiment is not very significant.

## 4.4 Summary
AC Milan official twitter can reveal the football world's important association. To compare the tweets of ACM and JUV, ACM is more focus on milan football, including the team news and derby news, while JUV is more related to the discussions on European football, including the transfer news and European Champions League news. And on Twitter, negative tweets about ACM are possibly to be more widely spread among football fans.